\documentclass[twocolumn,9pt]{article}

% Package imports
\usepackage{amsmath, amssymb, amsthm, graphicx, hyperref}
\usepackage{geometry, float}
\usepackage{tikz, pgfplots}
\usepackage{booktabs, array}
\usepackage{caption, subcaption}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{fancyhdr}
\usepackage{algorithm2e}
\usepackage{balance}

% TikZ libraries
\usetikzlibrary{decorations.pathmorphing, patterns, arrows, shapes, positioning, fit, calc}
\pgfplotsset{compat=1.16}

% Document setup
\geometry{margin=1in}
\setlength{\columnsep}{0.25in}
\setlength{\parindent}{1em}

% Header setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{A Constructive Spectral Framework for the Riemann Hypothesis}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Math definitions
\newcommand{\zs}{\zeta(s)}
\newcommand{\re}{\operatorname{Re}}
\newcommand{\im}{\operatorname{Im}}
\newcommand{\modm}{\bmod m}
\newcommand{\kbf}{\mathbf{k}}
\newcommand{\Hhat}{\hat{H}}

\title{A Constructive Spectral Framework for the Riemann Hypothesis\\via Symbolic Modular Potentials}
\author{Sebastian Schepis}
\date{\today}

\begin{document}

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
    We propose a novel spectral framework potentially related to the Riemann Hypothesis, constructing a finite-dimensional Hermitian operator whose eigenvalues numerically approximate the imaginary parts of the first few non-trivial zeros of the Riemann zeta function. The operator acts on a Hilbert space spanned by prime-indexed basis states and incorporates symbolic potentials derived from a discrete Schr\"odinger equation over modular residue classes, designed to reflect prime density. Numerical results for \(N=50\) show close alignment with the initial zeta zeros (squared loss \(\mathcal{L} \approx 0.00073\)). While cross-validation and scaling tests suggest robustness, this work remains a proof-of-concept. Establishing a rigorous connection to the Riemann Hypothesis requires significant further theoretical development and validation of the underlying conjectures regarding the infinite-dimensional limit and spectral properties.
    \end{abstract}
    \vspace{0.5cm}
  \end{@twocolumnfalse}
]

\input{sections/introduction.tex}

\input{sections/residue_class_potential_model.tex}

\input{sections/symbolic_schrodinger_equation.tex}

\input{sections/hermitian_operator_construction.tex}

\input{sections/numerical_spectral_analysis.tex}
\input{sections/ground_state_properties.tex}
\input{sections/self_adjointness.tex}
\input{sections/integrated_spectral_density.tex}
\input{sections/symbolic_resonance.tex}
\input{sections/operator_valued_zeta.tex}
\input{sections/spectral_riemann_hypothesis.tex}
\input{sections/discussion.tex}
\input{sections/appendix.tex}
\input{sections/acknowledgements.tex}

\begin{thebibliography}{9}
\bibitem{Connes1999} A. Connes, \textit{Trace formula in noncommutative geometry and the zeros of the Riemann zeta function}, Selecta Mathematica, 5(1), 29--106 (1999).
\bibitem{BerryKeating1999} M. V. Berry and J. P. Keating, \textit{The Riemann zeros and eigenvalue asymptotics}, SIAM Review, 41(2), 236--266 (1999).
\bibitem{Montgomery1973} H. L. Montgomery, \textit{The pair correlation of zeros of the zeta function}, Analytic Number Theory, AMS, 181--193 (1973).
\bibitem{HardyLittlewood1923} G. H. Hardy and J. E. Littlewood, \textit{The approximate functional equation in the theory of the zeta-function}, Mathematische Zeitschrift, 17, 1--37 (1923).
\bibitem{Davenport1980} H. Davenport, \textit{Multiplicative Number Theory}, 2nd ed., Springer (1980).
\end{thebibliography}

\balance


\end{document}